NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-12-06 RefereeReply1.txt

We would like to thank the referee for his/her constructive and valuable 
comments.  The points raised clearly helped us to further improve the 
quality of the manuscript.  Below we give detailed replies to the referee's 
queries and indicate the corresponding adjustments or additions to the 
manuscript.  We thereby follow the referee's initial ordering: 
1) The use of alpha(0) is motivated by the real emission that takes place at
   q^2=0. In order to obtain pole cancellation between the reals and the virtuals
   we chose the same factor for the virtual contribution. We are aware that there
   are other valid choices, however, at least in this case, the differences are small
   compared to the genuine electroweak corrections. We added a corresponding sentence
   about the motivation of the choice to the draft.
2) Renormalization- and factorization scale have been varied indepedently from 1/2 to 2 within 
   a 7 point scale variation, i.e. the combinations 0.5/2 and 2/0.5 are not present. The scale
   uncertainty has then be determined by the envelope of the various results.
   We added this information to the draft.
3) We added a sentence stating this explicitly.
4) The only analysis for three or more photons (Ref 6) focusses on heavy intermediate BSM
   particles. Therefore it did not make sense to adopt this set of cuts and we rather used generic
   cuts similar to the one applied for diphoton searches (i.e. asymmetric cuts between 1st and
   2nd photon). But they are not according to a specific experimental analysis. Nevertheless 
   they have been chosen in such a way that they are likely to be similar/comparable to a possible
   experimental analysis.
5)
6)
7)
8)  The figure captions have been corrected.
9)  This has been rephrased to clearly state which particles the invariant 
    mass cut acts on.
10) The PDFs have been specified, and the respective publication referenced.
11) 
12) The description of the observables has been enhanced in the following 
    cases:
    - Figure 6
    - Figures 8,11
13) We agree and added a sentence stating exactly that.

### 2017-12-06 results.tex
point 12

Finally, in Figure \ref{fig:aaa:dphi} we show the azimuthal 
separation $\Delta\phi$ between all three diphoton pairs. 
Similar features as before are visible as both the NLO QCD 
and NLO EW corrections relax the kinematic boundaries of 
the leading order calculation. 
Especially the azimuthal separation of the leading and 
third leading photon receives substantial shape corrections 
throughout the entire spectrum, with and without the 
presence of a jet veto. The angular distribution between leading photon
and the second or third subleading photon exhibit a kinematical edge at $\pi/2$ which 
is relaxed at NLO. 
This kinematical edge can be understood in the following way:
 Let us consider the first observable, the angular separation between 
the leading and the subleading photon, the argument also holds for the separation between
the leading and the third leading photon. The third leading photon has to recoil against the
system of the two leading photons. Let us go into the limit where the three photons have
a very similar transverse momentum and consider the configuration where the leading
photon is back-to-back to the third leading photon. Then the second photon must 
be perpendicular to this axis. If the third photon has less transverse momentum, it 
needs the second photon to recoil against the leading photon. Therefore it gets closer
to the third photon and further away from the leading photon. $\pi/2$ is therefore the
minimal distance the second photon can have to the leading one.  Only at NLO where
one can have additional radiation this constraint is relaxed. We will see later in Fig.
\ref{fig:aaz:dphi} that this situation is also present when one replaces one of the subleading
photons by a $Z$ boson. 
The electroweak corrections are negligible for this 
observable.

@@

Considering now the invariant mass of both photons 
and the leading photon and the lepton, presented in 
Figure \ref{fig:aaw:myy}, a similar picture 
presents itself. 
Both QCD corrections are moderate at small invariant 
masses and increase as the invariant mass rises. 
While $m_{\gamma_1\gamma_2}$ develops a correction 
factor of $\deltaQCD=2$ at 200\,GeV and then falls 
again to 0.4 at 1\,TeV, $m_{\gamma_1\ell}$ only 
reaches a maximum of $\deltaQCD=1.3$ before falling 
to 0.4 as well. 
In the presence of a jet veto, the shape of the corrections 
remains similar, but their magnitude is contained to 
be smaller than 0.5, turning negative around 500\,GeV 
for both observables. 
The electroweak corrections are again negative 
throughout, reaching $-15-20\%$ at invariant masses 
of 1\,TeV.
Again, above 200\,GeV they are consistently outside 
the LO uncertainty estimate and play an important 
role.

Figure \ref{fig:aaw:myy} also displays the transverse 
mass of the $W$ boson on the right hand side. 
This distribution exhibits the general features known 
from inclusive $W$ production, only the QCD corrections 
are scaled to the values present in this process.
Electroweak corrections are less pronounced than for 
the invariant masses, but are still non-negligible. 
They reach about $-8\%$ at $m_\text{T}=200\,\text{GeV}$ 
and $-14\%$ at 1\,TeV.

@@

Figure \ref{fig:aaz:myy} continues to display the invariant masses 
of the leading and subleading photon, and both the leading and 
subleading photon and the lepton pair. 
The familiar peak in $m_{\gamma_i\ell^+\ell^-}$ at the $Z$ boson mass 
is produced by 
configurations where the respective photon is emitted by the 
lepton-pair from a resonant $Z$ boson decay. 
Again, the QCD corrections are moderate, always staying below 
$\deltaQCD=0.4$ and of a similar shape as encountered already in 
\aaw\ production. 
The jet veto again reduces the QCD corrections and drives them negative 
in large portions of the observable range, reaching as much as 
$\deltaQCD=-0.5$ for the diphoton invariant mass. 
The electroweak corrections, on the other hand, are qualitatively very similar 
to the \aaw\ case: with the exception of the well known positive 
radiative corrections below the $Z$ peak, they are negative 
throughout, reaching $\deltaEW=-20\%$ at invariant masses of 
1\,TeV.
As in the case of the transverse momenta, due to the similar size 
of the QCD and electroweak corrections at large transverse 
momenta, the difference between their additive and the multiplicative 
combination is amplified.

>>>>

Finally, in Figure \ref{fig:aaa:dphi} we show the azimuthal 
separation $\Delta\phi$ between all three diphoton pairs. 
Similar features as before are visible as both the NLO QCD 
and NLO EW corrections relax the kinematic boundaries of 
the leading order calculation.Especially the azimuthal separation of the leading and 
third leading photon receives substantial shape corrections 
throughout the entire spectrum, with and without the 
presence of a jet veto. The angular distribution between leading photon
and the second or third subleading photon exhibit a kinematical edge at $\pi/2$ which 
is relaxed at NLO. 
This kinematical edge can be understood in the following way:
 Let us consider the first observable, the angular separation between 
the leading and the subleading photon, the argument also holds for the separation between
the leading and the third leading photon. The third leading photon has to recoil against the
system of the two leading photons. Let us go into the limit where the three photons have
a very similar transverse momentum and consider the configuration where the leading
photon is back-to-back to the third leading photon. Then the second photon must 
be perpendicular to this axis. If the third photon has less transverse momentum, it 
needs the second photon to recoil against the leading photon. Therefore it gets closer
to the third photon and further away from the leading photon. $\pi/2$ is therefore the
minimal distance the second photon can have to the leading one.  Only at NLO where
one can have additional radiation this constraint is relaxed. 
\revised{Therefore on finds that for the distributions involving the leading photon the particles
tend to be in a back-to-back configuration. This is most pronounced for the separation between
the two hardest photons and gets step by step relaxed by replacing the subleading by the third leading
photon and the leading by the subleading respectively.} We will see later in Fig.
\ref{fig:aaz:dphi} that this situation is also present when one replaces one of the subleading
photons by a $Z$ boson. 
The electroweak corrections are negligible for this 
observable.

@@

Considering now the invariant mass of both photons 
and the leading photon and the lepton, presented in 
Figure \ref{fig:aaw:myy}, a similar picture 
presents itself. 
Both QCD corrections are moderate at small invariant 
masses and increase as the invariant mass rises. 
While $m_{\gamma_1\gamma_2}$ develops a correction 
factor of $\deltaQCD=2$ at 200\,GeV and then falls 
again to 0.4 at 1\,TeV, $m_{\gamma_1\ell}$ only 
reaches a maximum of $\deltaQCD=1.3$ before falling 
to 0.4 as well. 
In the presence of a jet veto, the shape of the corrections 
remains similar, but their magnitude is contained to 
be smaller than 0.5, turning negative around 500\,GeV 
for both observables. 
The electroweak corrections are again negative 
throughout, reaching $-15-20\%$ at invariant masses 
of 1\,TeV.
Again, above 200\,GeV they are consistently outside 
the LO uncertainty estimate and play an important 
role. \revised{The change of shape due to the QCD corrections is
different compared to the three photon case where the QCD corrections 
are largest for small invariant masses and then continuously decrease with
higher masses. Due to the presence of a heavy gauge boson additional radiation
shifts the invariant mass towards higher values.}
Figure \ref{fig:aaw:myy} also displays the transverse 
mass of the $W$ boson on the right hand side. 
This distribution exhibits the general features known 
from inclusive $W$ production, only the QCD corrections 
are scaled to the values present in this process.
Electroweak corrections are less pronounced than for 
the invariant masses, but are still non-negligible. 
They reach about $-8\%$ at $m_\text{T}=200\,\text{GeV}$ 
and $-14\%$ at 1\,TeV.

@@

Figure \ref{fig:aaz:myy} continues to display the invariant masses 
of the leading and subleading photon, and both the leading and 
subleading photon and the lepton pair. \revised{For the invariant mass of the
two leading photons one also observes a shift towards higher invariant masses
in the presence of QCD corrections as seen in Fig. \ref{fig:aaw:myy}. The effect
is less pronounced due to the fact that there is also a triple photon process contributing
to the dilepton final state. The observed pattern is therefore a mixture between what
can be seen in Fig. \ref{fig:aaa:myy} and the results in Fig. \ref{fig:aaw:myy}.}
The familiar peak in $m_{\gamma_i\ell^+\ell^-}$ at the $Z$ boson mass 
is produced by 
configurations where the respective photon is emitted by the 
lepton-pair from a resonant $Z$ boson decay. 
Again, the QCD corrections are moderate, always staying below 
$\deltaQCD=0.4$ and of a similar shape as encountered already in 
\aaw\ production. 
The jet veto again reduces the QCD corrections and drives them negative 
in large portions of the observable range, reaching as much as 
$\deltaQCD=-0.5$ for the diphoton invariant mass. 
The electroweak corrections, on the other hand, are qualitatively very similar 
to the \aaw\ case: with the exception of the well known positive 
radiative corrections below the $Z$ peak, they are negative 
throughout, reaching $\deltaEW=-20\%$ at invariant masses of 
1\,TeV.
As in the case of the transverse momenta, due to the similar size 
of the QCD and electroweak corrections at large transverse 
momenta, the difference between their additive and the multiplicative 
combination is amplified.
